---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CovidYe

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-Year-97/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-Year-97/actions)
<!-- badges: end -->

CovidYe package is created by Chengzhi Ye, which is followed strictly by the package-instructions. It contains one Shiny App, one data set and three functions. The main purpose of CovidYe package is to provide the basic information about COVID-19 of the countries with most confirmed cases and some functions to create the interactive plots and tables which are contains in the Shiny App.

## Installation & Implementation

<!-- You can install the released version of CovidYe from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("CovidYe") -->
<!-- ``` -->

The development version can be installed from my [GitHub](https://github.com/etc5523-2020/r-package-assessment-Year-97) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-Year-97")
```

After installing `CovidYe` package, you can type `launch_app()` in the console to run the `Covid-19` Shiny App.

## Example

### A simple presentation of coronavirus data set:

```{r, include=FALSE}
library(CovidYe)
library(tibble)
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)


```

```{r example, echo=FALSE, warning=FALSE}
as_tibble(coronavirus)
```

### The Daily Situation and Cumulative Cases

```{r, echo=FALSE, warning=FALSE}
coronavirus %>% 
  select(date, country, type, cases) %>% 
  group_by(type, date) %>%
  summarise(total_cases = sum(cases)) %>%
  pivot_wider(names_from = type, values_from = total_cases) %>%
  arrange(date) %>%
  mutate(totalconfirmed = cumsum(confirmed),
         totalrecovered = cumsum(recovered),
         totaldeath = cumsum(death)) %>% 
  head(10) %>% 
  kableExtra::kable()

```

### The overall change trend of COVID-19

```{r, warning=FALSE, echo=FALSE}
coronavirus %>% 
   select(date, country, type, cases) %>% 
  filter(country %in% c("US", "India", "Brazil", "Russia", "Peru")) %>% 
  filter(type == "confirmed") %>% 
  ggplot(aes(x = date, y = cases, color = country, lable = country)) +
  
  geom_line() +
  theme_bw()


```


## More Info about CovidYe Package

The complete information and instruction can be seen in [my pkgdown website](https://etc5523-2020.github.io/r-package-assessment-Year-97/). 

Also there is a [distill blog](https://gifted-joliot-89880e.netlify.app/shiny.html) which is also designed by me. You can learn more information about my Shiny App and the COVID-19 basic situation in that site. Therefore, you are welcome to have a look. 

