---
title: "General Situation of COVID-19 in the world"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{General Situation of COVID-19 in the world}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8.5,
  fig.height = 7
)
```

This vignette can describe the use of the `CovidYe` package, including how to launch the shiny application, what the application can do, and the guidelines for its users. 

## Installing CovidYe

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-Year-97")
```

## Launching shiny app

The main goal of `CovidYe` package is to provide a shiny app called Covid-19 to convey the daily information of Covid-19 in `r length(unique(CovidYe::coronavirus$country))` countries and the overall trend of different type of cases.

```{r, include=FALSE}
library(CovidYe)
library(tibble)
library(dplyr)
library(tidyr)
library(plotly)
```

```{r launching, eval=FALSE}
launch_app()
```

## Exploration of the data in the CovidYe package

This package also provides the `coronavirus` dataset, which contains daily information for 118 countries over time. This data is sourced from [WHO](https://www.who.int/) and [coronavirus](https://github.com/RamiKrispin/coronavirus).

The following table and interactive plot are provided by the functions contained in that Shiny app. The visualization effects of displaying Covid-19 general information are attractive for the users. 

### The Daily Situation and Cumulative Cases:

```{r, echo=FALSE, warning=FALSE}
coronavirus %>% 
  select(date, country, type, cases) %>% 
  group_by(type, date) %>%
  summarise(total_cases = sum(cases)) %>%
  pivot_wider(names_from = type, values_from = total_cases) %>%
  arrange(date) %>%
  mutate(totalconfirmed = cumsum(confirmed),
         totalrecovered = cumsum(recovered),
         totaldeath = cumsum(death)) %>% 
  head(15) %>% 
  kableExtra::kable(align = 'lrrrrrr', 
                     format.args = list(big.mark = ",")) %>% 
   kableExtra::kable_styling(
     font_size = 15,
     bootstrap_options = c("striped", "hover", "condensed")) 

```

### The overall change trend of COVID-19: 

```{r, echo=FALSE, warning=FALSE}
corona_daily <- coronavirus %>% 
  select(date, country, type, cases) %>% 
  group_by(type, date) %>%
  summarise(total_cases = sum(cases)) %>%
  pivot_wider(names_from = type, values_from = total_cases) %>%
  arrange(date) %>%
  mutate(totalconfirmed = cumsum(confirmed),
         totalrecovered = cumsum(recovered),
         totaldeath = cumsum(death))

g <- plot_ly(corona_daily, 
                 x = ~ date, 
                 y = ~ totalconfirmed,
                 name = 'Confirmed',
                 fillcolor = 'pink',
                 type = 'scatter',
                 mode = 'none',
                 stackgroup = 'one') %>% 
      add_trace(y = ~totalrecovered, 
                name = 'Recovered', 
                fillcolor = 'lightgreen') %>%
      add_trace(y = ~ totaldeath, 
                name = "Death",
                fillcolor = 'black') %>%
      layout(title = "Distribution of Covid19 Cases Worldwide",
             legend = list(x = 0.1, y = 0.9),
             yaxis = list(title = "Number of Cases"),
             xaxis = list(title = "Date"),
             hovermode = "compare")
    
    ggplotly(g)
```

### The Current Situation of COVID-19 in Top 10 countries with most confirmed cases:

```{r bubblemap, echo=FALSE, warning=FALSE}
coronavirus_new <- coronavirus %>% 
  group_by(country, type) %>%
  summarise(total_cases = sum(cases)) %>%
  pivot_wider(names_from = type, values_from = total_cases) %>%
  arrange(-confirmed) %>%
  head(20) %>%
  mutate(recover_rate = recovered / confirmed,
         death_rate = death / confirmed) %>%
  ungroup() 


  plotly::plot_ly(y = ~ round(100 * coronavirus_new$recover_rate, 1),
                  x = ~ round(100 * coronavirus_new$death_rate, 1),
                  size = ~  log(coronavirus_new$confirmed),
                  sizes = c(5, 70),
                  type = 'scatter', 
                  mode = 'markers',
                  color = ~ coronavirus_new$country,
                  marker = list(sizemode = 'diameter' , opacity = 0.5),
                  hoverinfo = 'text',
                  text = ~paste("</br>", coronavirus_new$country, 
                                "</br> Confirmed Cases: ", coronavirus_new$confirmed,
                                "</br> Recovery Rate: ", paste(round(100 * coronavirus_new$recover_rate, 1), "%", sep = ""),
                                "</br> Death Rate: ",  paste(round(100 * coronavirus_new$death_rate, 1), "%", sep = ""))) %>%
  plotly::layout(yaxis = list(title = "Recovery Rate", ticksuffix = "%"),
                 xaxis = list(title = "Death Rate", ticksuffix = "%", 
                              dtick = 1, 
                              tick0 = 0)) 
```

Also there are two functions after refactoring in the package which can simplify the input selection in the Shiny app and the process of making formatted tables. You can find that in the pckdown site.













